Bib Library

### 2024-05-20 studies/library_formatter.qmd
Resolving our pass3 issues

```{r}
# read in bibtex library as data frame
bib_df_ca <- bib2df::bib2df('metaMER_lib_third_pass_ca.bib')
bib_df_te <- bib2df::bib2df(blahblah)

@@

```{r}
# remove columns only belonging to one database
bib_df_ca$UNIQUE.ID <- NULL
bib_df_ca$C1 <- NULL
# remove unnecessary column
bib_df_ca$HASABSTRACT <- FALSE
# relevel priority column with intuitive names
bib_df_ca$PRIORITY <- as.factor(bib_df_ca$PRIORITY)
levels(bib_df_ca$PRIORITY) <- c('high_priority', 'low_priority')
bib_df_ca$PRIORITY <- plyr::revalue(bib_df_ca$PRIORITY, 
                                    c(prio1 = 'high_priority',
                                      prio3 = 'low_prioirty'))
# make casing consistent
bib_df_ca$SOURCE <- tolower(bib_df_ca$SOURCE)
# consistent names for private notes
names(bib_df_ca)[names(bib_df_ca) == 'comment_camja'] <- 'NOTES.CA'
```

@@

```{r}
# select bibkey (for merge) and notes from second reviewer
bib_df_te <- bib_df_te %>% select(BIBTEXKEY, NOTES.TE)

@@

```{r}
bib2df::df2bib(bib_df_merged, file = 'metaMER_lib_third_pass_clean.bib')
```

##

>>>>

```{r}
# read in bibtex library as data frame
bib_df_ca <- bib2df::bib2df('metaMER_library_third_pass_ca.bib')
bib_df_te <- bib2df::bib2df('metaMER_library_third_pass_te.bib')
bib_df_ca <- dplyr::filter(bib_df_ca,PRIORITY=='prio1')
bib_df_te <- dplyr::filter(bib_df_te,PRIORITY=='prio1')
sum(bib_df_ca$BIBTEXKEY %in% bib_df_te$BIBTEXKEY)==nrow(bib_df_ca)
```

@@

```{r}
# remove columns only belonging to one database
bib_df_ca$UNIQUE.ID <- NULL
bib_df_ca$C1 <- NULL
# remove unnecessary column
bib_df_ca$HASABSTRACT <- NULL
# relevel priority column with intuitive names
# bib_df_ca$PRIORITY <- as.factor(bib_df_ca$PRIORITY)
#levels(bib_df_ca$PRIORITY) <- c('high_priority', 'low_priority')
# bib_df_ca$PRIORITY <- plyr::revalue(bib_df_ca$PRIORITY, 
#                                     c(prio1 = 'high_priority',
#                                       prio3 = 'low_prioirty'))
# make casing consistent
bib_df_ca$SOURCE <- tolower(bib_df_ca$SOURCE)
# consistent names for private notes
names(bib_df_ca)[names(bib_df_ca) == 'COMMENT.CAMJA'] <- 'NOTES.CA'
```

@@

```{r}

# select bibkey (for merge) and notes from second reviewer
bib_df_te <- bib_df_te %>% select(BIBTEXKEY, NOTES.TE)

@@

```{r}
# JOURNAL and JOURNALTITLE are the same (latter for scopus)

dim(bib_df_merged)
bib2df::df2bib(bib_df_merged, file = 'metaMER_lib_third_pass_clean.bib')

```
## Next

Compare pass 3 annotations and resolve conflicts (`pass 3 comparison.qmd`)
